Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-07 bbbq_article.tex
More neutral wording

The earlier study uses a hand-crafted method, that only works on MHC-I.
Instead, we use MHCnuggets, which (1) free and open source, and (2) predicts
IC50s on both MHC-I and MHC-II.

>>>>

The earlier study uses a hand-crafted method, 
that has been trained on MHC-I haplotypes only.
This study uses MHCnuggets, which (1) free and open source, and (2) predicts
IC50s on both MHC-I and MHC-II.
